\documentclass[nocc]{template/openetcs_article} 
\usepackage{longtable}
\usepackage{ifthen}
\usepackage{hyperref}
\usepackage{tabularx}

\graphicspath{{./template/}{.}{./images/}}

\input{macros.tex}

\begin{document}
\frontmatter
\project{openETCS}

%Please do not change anything above this line
%============================
% The document metadata is defined below

%assign a report number here
\reportnum{OETCS/WP6/D6.1}

%define your workpackage here
\wp{Work-Package 6: ``Dissemination, Exploitation and Standardization''}

%set a title here
\title{Dissemination Plan and Report}

%set a subtitle here
\subtitle{First version of the project Dissemination Plan (D6.1)}

%set the date of the report here
\date{March 2013}

%define a list of authors and their affiliation here


\author{Dr. Michael Ditze \and Dr. Stefan Rieger}

\affiliation{TWT GmbH\\
Science \& Innovation\\
Bernhäuser Straße 40-42\\
D-73765 Neuhausen\\
Germany
}


\author{Dr. Frank Golatowski}

\affiliation{
University of Rostock\\
Faculty of Computer Science and Electrical Engineering\\
Institute of Applied Mikroelektronics and Computer Engineering\\
Richard-Wagner Str. 31\\
18119 Rostock-Warnemuende\\
Germany
}

\author{Dr. Peter Mahlmann}

\affiliation{
DB Netz AG\\
Völckerstraße 5\\
D-80939 München\\
Germany
}


\author{Hansj\"org Manz \and Jan Welte}

\affiliation{Technische Universit\"at Braunschweig\\
  Institute for Traffic Safety and Automation Engineering\\
  Langer Kamp 8\\
  D-38106 Braunschweig\\
  Germany}
  
  
\author{\red{@all: Add your name if you contributed}}

\affiliation{\red{@all: Add your affiliation if you contributed}}
  
% define the coverart
\coverart[width=350pt]{chart}

%define the type of report
\reporttype{Deliverable}


\begin{abstract}
This document is the first version of the openETCS dissemination plan and report. It represents a preliminary version of the project dissemination strategy and covers past and as well as planned dissemination activities. There will be two updated versions to this document (D6.3 and D6.5).
\end{abstract}

%=============================
%Do not change the next three lines
\maketitle
\tableofcontents
%\listoffiguresandtables
\newpage
%=============================

% The actual document starts below this line
%=============================



\input{sections/introduction.tex}

\input{sections/past_activities.tex}

\input{sections/exhibitions.tex}

\input{sections/conferences_external.tex}
 
\input{sections/journals.tex}

\input{sections/conferences_openetcs.tex}

%Removed from the document -> exploitation plan 
%\input{sections/standardisation.tex}
 
\input{sections/open_source.tex}

\input{sections/further_activities.tex}

%Removed from the document
%\input{sections/communication.tex}

%=============================

\nocite{*}

\bibliographystyle{unsrt}
\bibliography{erdc}



\begin{thebibliography}{9}



\end{thebibliography}

%===================================================
%Do NOT change anything below this line

\end{document}
