\section{Further Activities}\label{sct:further_activities}

\subsection{openETCS Website}
The project's public website is available at \url{http://www.openetcs.org}. In addition to a brief overview over the project, its goals and the participating partners, it provides links to the openETCS working platform GitHub \cite{github}, enabling easy access to deliverables, software, meeting minutes, etc. Moreover, a calendar with upcoming events gives people not yet involved but interested in the project an overview of ongoing activities and thus the possibility to participate in these events. The website also offers downloads for the openETCS tool.



\subsection{GitHub}

Throughout the project the GitHub platform \cite{github} is used for management and publication of project results. Most of the project repositories are public and thus are accessible to the outside world, making it possible for everyone to view the state of the project and its results. In addition, the platform enables anybody to contribute content to the project. GitHub is based on the open source Git tool \cite{gittool} and provides a wide variety of functions, including versioning, team collaboration support, public and private repositories and a wiki. In addition to the main project repositories wikis are a useful tool for communicating project state and results to the outside world.

\subsection{Twitter}

An openETCS Twitter account has been set up and is available at \url{https://twitter.com/openetcs}. Here, news about the project, events, release of deliverables and milestones, etc.~are communicated. As of September 2014 the Twitter account is followed by about 200 users.

\subsection{YouTube}

An openETCS YouTube Channel is available at \url{https://www.youtube.com/user/openETCS}. Via this channel recordings of online trainings are available to the public. The trainings cover topics such as Git practices, SysML model checks, and a guideline how to set up eclipse to build the openETCS tool for potential contributors.

%%In Exploitation Plan
%\subsection{Registered association (eingetragener Verein)}
%\tbc[by DB]


%%Currently no plans
%\subsection{Press Releases}
%\tbc[by DB]

