\section{Introduction}

This document is the second (updated) version of the openETCS dissemination plan and report. It represents the project dissemination strategy and covers past and as well as planned dissemination activities.

\paragraph{Objectives and Achievements}
The dissemination of the project results will leverage the industrial, academic and societal awareness of the project, support the establishment of eco-systems of stakeholders and encourage the exchange of research results, thus contributing to the paradigm of open innovation. Dissemination activities include (but are not limited to) website setup, publication of project results at conferences and in journals, organisation of workshops, exhibitions and demonstrations.

After the release of the first version of the dissemination plan and report, a plethora dissemination activities have been conducted, including publications of project partners and presentations at significant conferences. In particular, the openETCS project was presented at InnoTrans 2014, the world's largest trade fair in the railway industry. The InnoTrans activities included a special openETCS session in the ``Speakers' Corner'', the public openETCS mid-term workshop and the presentation of results at partners' booths.

\paragraph{Structure of this Document}
The document is structured as follows. Section~\ref{sct:past_activities} lists dissemination activities categorised by their type (conference, exhibition, journal, etc.). Details like date, publisher and/or venue as well as contributors and an abstract are provided. Section~\ref{sct:planned_activities} is devoted to the future dissemination strategy. Here we list planned future dissemination opportunities and events.

Section \ref{sct:further_activities} addresses additional dissemination activities not covered by the other sections.
