\section{Exhibitions and Trade Shows}\label{sct:exhibitions}

\begin{activity}{ITEA \& ARTEMIS Co-summit 2013}
	\entry{Date}{4-5/12/2013}
	\entry{Location}{Stockholm, Sweden}
	%\entry{Interested Partners}{Alstom, Deutsche Bahn, ERSA, ERTMS-Solutions, General Electric, Siemens, SNCF}
	\desc{The ITEA \& ARTEMIS Co-summit will be used as platform to present the project, report about the current status of the openETCS project and present first results. It is a great opportunity for exchanging ideas with the community and to disseminate and advertise the project as the event covers participants from industry, academia, public authorities and press from all over Europe.}
\end{activity}

\begin{activity}{INNOTRANS}
	\entry{Date}{2014}
	\entry{Location}{Berlin, Germany}
	%\entry{Interested Partners}{Alstom, Deutsche Bahn, ERSA, ERTMS-Solutions, General Electric, Siemens, SNCF}
	\desc{INNOTRANS will provide an opportunity to present key results, e.g. modelling tools and simulators. INNOTRANS, the world's largest trade fair for railways and public transit, addressing the entire railway industry. Since several openETCS partners like Alstom, Deutsche Bahn, ERSA, ERTMS-Solutions, General Electric, Siemens, SNCF, etc. are regularly represented at that industrial fair, the openETCS subject could be featured specifically at their particular exhibition having a best possible outreach to make the approach well known.}
\end{activity}


\begin{activity}{Embedded World Exhibition \& Conference}
	\entry{Frequency}{annual}
	\entry{Next Event}{March 2013 (Nuremberg, Germany)}
	\website{http://www.embedded-world.eu/}
	%\entry{Interested Partners}{Fraunhofer ESK}
	\desc{The annual EmbeddedWorld Exhibition \& Conference is the world largest trade exhibition in the area of embedded systems. It is planned to present openETCS partner results at the exhibition as well as at the conference.}
\end{activity}

\begin{activity}{Rencontre du numérique de l'ANR}
	\entry{Frequency}{annual}
	\entry{Next Event}{April 2013 (Paris, France)}
	%\entry{Interested Partners}{CEA LIST}
	\desc{Presentation of (French) projects related to openETCS; CEA LIST plans to present the Frama-C tool.}
\end{activity}
