\section{Journals and Magazines}\label{sct:journals}


\begin{activity}[past]{European Railway Review, Volume 18, Issue 3, 2012}
	\entry{Type of Contribution}	{Article}
	\entry{Title}	{openETCS: Applying `Open Proofs' to European Train Control}
	\entry{Pages} {30--34}
	\entry{Author}	{Klaus-R\"{u}diger Hase (DB)}
	\entry{Publischer} {Russell Publishing Ltd., Kent, UK}
\website{http://europeanrailwayreview.com/tag/openetcs}
	\desc{European Railway Review is the leading bi-monthly technical journal for the European rail industry. Featuring articles and news about the latest technologies and developments, the magazine is essential reading for people involved in the railway business. Here, an overview article of the openETCS project, covering the technical background and the project goals, has been published by DB Netz AG.}
\end{activity}

\begin{activity}{Networking Sciences}
	\entry{Interested Partners}{Institut Telecom}
	\desc{\tbc[by Institut Telecom]}
\end{activity}

\begin{activity}{Annals of Telecommunications}
	\entry{Interested Partners}{Institut Telecom}
	\desc{\tbc[by Institut Telecom]}
\end{activity}

\begin{activity}{Computer Networks}
	\entry{Interested Partners}{Institut Telecom}
	\desc{\tbc[by Institut Telecom]}
\end{activity}

\begin{activity}{Journal of Statistical Software}
	\website{http://www.jstatsoft.org/}
	\entry{Interested Partners}{Institut Telecom}
	\desc{\tbc[by Institut Telecom]}
\end{activity}

\begin{activity}{Software Tools for Technology Transfer (STTT)}
	\website{http://sttt.cs.uni-dortmund.de/}
	\entry{Interested Partners}{CEA LIST}
	\desc{\tbc[by CEA LIST]}
\end{activity}

\begin{activity}{SIGNAL+DRAHT}
	\website{http://www.eurailpress.de/verlag/zeitschriften/signal-draht/profil.html}
	\desc{\red{@all, especially DB: Check whether this is still relevant, then please complete it. Otherwise it will be removed.}}
\end{activity}

\begin{activity}{International Railway Journal (IRJ)}
	\website{http://www.railjournal.com}
	\desc{\red{@all, especially DB: Check whether this is still relevant, then please complete it. Otherwise it will be removed.}}
\end{activity}


\begin{activity}{Eisenbahntechnische Rundschau (ETR)}
	\website{http://www.eurailpress.de/verlag/zeitschriften/eisenbahntechnische-rundschau/profil.html}
	\desc{\red{@all, especially DB: Check whether this is still relevant, then please complete it. Otherwise it will be removed.}}
\end{activity}

\begin{activity}{ZEV Rail}
	\website{http://www.zevrail.de}
	\desc{\red{@all, especially DB: Check whether this is still relevant, then please complete it. Otherwise it will be removed.}}
\end{activity}




-
